FITS format for planetary surfaces: definitions, applications and best practices.

### 2018-02-28 ess_marmo.tex
Update on Overleaf.

\affiliation{1}{GEOPS, Univ. Paris-Sud, CNRS, Univ. Paris-Saclay,
Orsay, France}
\affiliation{2}{U. S. Geological Survey, Astrogeology Science Center,
Flagstaff, AZ, USA}
\affiliation{3}{LESIA, Observatoire de Paris, Universit\'e PSL, CNRS, Sorbonne Universit\'e,
Univ. Paris Diderot, Sorbonne Paris Cit\'e, 5 place Jules Janssen, 92195 Meudon, France}
\affiliation{4}{Jacobs University, Bremen, Germany}
\affiliation{5}{Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l'Universit\'e, 67000, Strasbourg, France}
\affiliation{6}{ASI Science Data Center, c/o ASI, Via del Politecnico snc, 00133, Rome, Italy}
\affiliation{7}{INAF-OAR, Via Frascati n. 33, 00078, Monte Porzio Catone (RM), Italy}

@@

VO-QGIS-plugin\footnote{https://github.com/epn-vespa/VO\_QGIS\_plugin}

>>>>

\affiliation{1}{GEOPS, Univ. Paris-Sud, CNRS, Univ. Paris-Saclay,
Orsay, France}
\affiliation{2}{U. S. Geological Survey, Astrogeology Science Center,
Flagstaff, AZ, USA}
\affiliation{3}{LESIA, Observatoire de Paris, Universit\'e PSL, CNRS, Sorbonne Universit\'e,
Univ. Paris Diderot, Sorbonne Paris Cit\'e, 5 place Jules Janssen, 92195 Meudon, France}
\affiliation{4}{Jacobs University, Bremen, Germany}
\affiliation{5}{Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l'Universit\'e, 67000, Strasbourg, France}
\affiliation{6}{Space Science Data Center - ASI, Via del Politecnico snc, 00133, Rome, Italy}
\affiliation{7}{INAF-OAR, Via Frascati n. 33, 00078, Monte Porzio Catone (RM), Italy}

@@

\subsection{FITS and QGIS}
QGIS is a largely used open source geospatial analysis software.
It is using GDAL for layer import: QGIS is then already capable to display FITS files,
making use of a Virtual GDAL header, as described above.
Once implemented in GDAL, FITS will officially become a supported format by QGIS.

In addition to that, a QGIS plugin has been developed\footnote{https://github.com/epn-vespa/VO\_QGIS\_plugin}
\citep{Minin} in order to download and display files exposed via EPN-TAP servers.
